---
title: "Bechdel Test"
author: "Created by Mine Çetinkaya-Rundel"
output: html_document
---
<!--- you might change html_document to github_document if you are working with GitHub--->

```{r setup, include = FALSE}
knitr::opts_chunk$set(comment = "")
```


In this mini analysis we work with the data used in the FiveThirtyEight story titled ["The Dollar-And-Cents Case Against Hollywood's Exclusion of Women"](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/).

1. Your task is to fill in the blanks denoted by `___` with text or code.  
2. Fix any errors.  
3. Identify specific R code function and how you looked them up.  

## Data and packages

We start with loading the packages we'll use.

```{r load-packages, message=FALSE}
library(fivethirtyeight)
library(tidyverse)
```


The dataset contains information on `r nrow(bechdel)` movies released between `r min(bechdel$year)` and `r max(bechdel$year)`.  
However we'll focus our analysis on movies released between 1990 and 2013.

```{r}
bechdel90_13 <- bechdel %>%  
  filter(between(year, 1990, 2013))
```

> What is the `%>%` inside the code? What does it do? How did you determine your answer?  
The `%>%` inside the code is a pipe operator. It feeds information to the next line. I determined my answer by noticing that the `filter` function requires us to include the data set but it is not included within the function so the `%>%` must be telling it to use the dataset we established in that previous line.  
  
  
  
There are `1615` such movies.

The financial variables we'll focus on are the following:

-   `budget_2013`: Budget in 2013 inflation adjusted dollars
-   `domgross_2013`: Domestic gross (US) in 2013 inflation adjusted dollars
-   `intgross_2013`: Total International (i.e., worldwide) gross in 2013 inflation adjusted dollars

And we'll also use the `binary` and `clean_test` variables for **grouping**.

## Analysis

Let's take a look at how median budget and gross vary by whether the movie passed the Bechdel test, which is stored in the `binary` variable.

```{r message = FALSE}
bechdel90_13 %>%
  group_by(binary) %>%
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

> What does `summarise()` do? How did you look it up?  
According to the description of `summarise()` which I looked up under Help, it "creates a new data frame" and has "one column for each grouping variable and one column for each of the summary statistics [...] specified." In other words, `summarise()` allows us to see a table that displays the summary statistics we input into the function.  



Next, let's take a look at how median budget and gross vary by a more detailed indicator of the Bechdel test result.  
This information is stored in the `clean_test` variable, which takes on the following values:

-   `ok` = passes test
-   `dubious`
-   `men` = women only talk about men
-   `notalk` = women don't talk to each other
-   `nowomen` = fewer than two women

```{r message = FALSE}
bechdel90_13 %>%
  group_by(clean_test) %>%  #fill in the gap with the right variable
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

In order to evaluate how return on investment varies among movies that pass and fail the Bechdel test, we'll first create a new variable called `roi` as the ratio of the gross to budget.

```{r}
bechdel90_13 <- bechdel90_13 %>%
  mutate(roi = (intgross_2013 + domgross_2013) / budget_2013)
```


Let's see which movies have the highest return on investment.

```{r}
bechdel90_13 %>%
  arrange(desc(roi)) %>% 
  select(title, roi, year)
```

> What does `select()` do? How did you look it up?  
Using `select()` allows us to be able to chose what part of the data we want to show. For example, althought the `bechdel90_13` dataset has 16 different variables, the table above only shows th three we've selected. I found [this lesson](https://study.com/academy/lesson/select-function-in-r-programming.html) to help with my understanding of how the `select()` function works.  




Below is a visualization of the return on investment by test result, however it's difficult to see the distributions due to a few extreme observations.

```{r warning = FALSE}
ggplot(data = bechdel90_13, 
       mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       x = "Detailed Bechdel result",
       y = "Return on Investment",
       color = "Binary Bechdel result")
```
  
  
What are those movies with *very* high returns on investment?

```{r}
bechdel90_13 %>%
  filter(roi > 400) %>%
  select(title, budget_2013, domgross_2013, year)
```
  
Zooming in on the movies with `roi < 15` provides a better view of how the medians across the categories compare:
  
```{r warning = FALSE}
ggplot(data = bechdel90_13, mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       subtitle = "Return on Investement < 15", # Something about zooming in to a certain level
       x = "Detailed Bechdel result",
       y = "Return on investment",
       color = "Binary Bechdel result") +
  coord_cartesian(ylim = c(0, 15))
```
  
  
> What did you learn from the data analysis included in the document?  
From the table where we are able to see whether a movie passed or failed the bechdel test, I was able to notice that the movies that failed on average had higher budgets and higher domestic and international gross earnings than those movies that passed the bechdel test.
However, I saw that whether a movie passes or fails the test doesn't seem to have much effect on the return on investments since the distribution of the ok is about the same as the others. The one difference is that ok seems to have a higher maximum when looking into `roi < 15`. That is what I was able to learn about the data analysis included in the document.


